Attributions for Poverty in Post-Socialist Countries

### 2014-03-02 article2013.Rmd
5.3 results ok
Muutin tekstissä taulukon 5 liitetaulukoksi 1. Se jää nykyisellään niin pieneen rooliin että sen voisi siirtää liitetaulukoksi. Mikäli sen haluaa pitään taulukko 5:na niin pitäisi kirjoitella vähän enemmän lihaa luiden ympärille eli avata sitä enemmän.

We are modelling the date in stepwise manner first running the empty models for both social blame (Table 3) and individual blame (Table 4) type of explanation. At second stage we include all individual-level predictors and in third stage we include only the macro-level predictors. In final models we include both the individual and macro-level variables. As we are using *logistics regression* instead of *multinomial logistic regression* with dependent variable of nominal scale, we confirm our findings by running a further model where we predict the support for social blame against the support for individual blame using both the individual and contextual level variables. This model is compared with full models from tables 3 and 4 in Table 5.

@@

Including only the contextual level predictors, as in models *SB contextual* (table 3) and *IB contextual* (table 4), has a marginal effect on deviance when comparing with empty models, but a substantial effect on between country variance. Of the contectual predictors the change in GDP has the most significant impact on dependent variables in a such manner, that the better national economy has performed during the crises the less there is support for social blame type of explanation, and in opposite way in regard to individual blame.

Introduction of both the individual and contextual level predictors in the models has only a minor impact on significange of the predictors. Same individual level predictors; *perceived low income*, *negative expectations for future*, *perception of negative impacts of economic crises* and *benefit dependency* remain significant at the individual level and *change in national GDP* at the contextual level. As for overall model fit the individual level predictors are in key role: the impact of contextual level variables on deviance is only -10 and -16 for social blame and individual blame type of explanation, respectively. Model *SB vs. IB* in table 5 confirms the findings on the significange and direction of the association.

>>>>

We are modelling the date in stepwise manner first running the empty models for both social blame (Table 3) and individual blame (Table 4) type of explanation. At second stage we include all individual-level predictors and in third stage we include only the macro-level predictors. In final models we include both the individual and macro-level variables. As we are using *logistics regression* instead of *multinomial logistic regression* with dependent variable of nominal scale, we confirm our findings by running a further model where we predict the support for social blame against the support for individual blame using both the individual and contextual level variables. This model is compared with full models from Tables 3 and 4 in Appendix Table 1.

@@

Descriptive figures indicated rather clear associations between country-level contextual factors and perceptions of the causes of poverty. Tables 3 and 4 show that inclusion of only the contextual level determinants to the models (SB contextual and IB contextual respectively) has a marginal effect on deviance when the models are compared to empty models, but a substantial effect on between country variance. The change in GDP has the most significant impact on attributions for poverty. In line with our hypothesis, the larger the economic growth in a country is, more likely people are to blame the poor themselves and less likely they endorse injustice in society as a reason for poverty.

Interesting enough, however, results show that unlike descriptive statistics indicated neither country-level living conditions (measured by Human Development Index) nor the level of goodness of government are significantly associated with attributions for poverty. In addition, final models in Tables 3 and 4 show that inclusion of both the individual and contextual level predictors to the models has only a minor impact on significance of the predictors. Consequently, at the individual-level *perceived low income*, *negative expectations for future*, *perception of negative impacts of economic crisis* and *benefit dependency* and at the contextual level *change in national GDP* remain significant determinants for the perceptions of the causes of poverty. The findings on the significance and direction of the association are confirmed in Appendix Table 1 which examines the predictive power of the support for social blame against the support for individual blame using both the individual and contextual level variables.
